---
title: "Data Preparation - Panel"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
      number_sections: yes
    code_folding: show
    number_sections: yes
editor_options:
  chunk_output_type: console
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = TRUE,
                      cache = FALSE
                      )
options(scipen=9999) # desactivar notacion cientifica
```



# Libraries

```{r}
# if (!require("pacman")) install.packages("pacman") # package manager
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               haven,       # importar datos en .dta o .sav
               car,         # recodificar variables
               sjlabelled,  # etiquetado de variables
               sjmisc,      # descriptivos y frecuencias
               sjPlot,      # tablas, plots y descriptivos
               summarytools, # resumen de dataframe
               responsePatterns # detect careless resp.)
)

```

# Data

```{r}
data <- read_dta("01-input/data/original/panel_firstwave/zhp_anchor_bv1_0.dta")

```

There are `r nrow(data)` observations and `r ncol(data)` variables.

## Search & select variables

```{r}
find_var(data = data,"cohes")
find_var(data = data,"id")

data_cohes <- data %>% dplyr::select(pid,pcohes01:pcohes12) # pid: person ID

sjlabelled::get_label(data_cohes)
```

# Original data summary

```{r}
print(dfSummary(data_cohes, headings = FALSE), method = "render")
```

# NAs

```{r}
frq(data_cohes$pcohes01) # check NAs
```

Negative values to NA

```{r}
data_cohes <- data_cohes %>% set_na(pcohes01:pcohes12, na = c(-9:-1), drop.levels = TRUE)
```

# Set labels

## English value labels

```{r}
data_cohes <- data_cohes %>% set_labels(pcohes01:pcohes12, labels = c("Not at all", "Rather not","In part", "Rather so", "Totally"))

```

## English variable labels

```{r}
data_cohes$pcohes01 <- set_label(x = data_cohes$pcohes01, label = "Place in society")
data_cohes$pcohes02 <- set_label(x = data_cohes$pcohes02, label = "Develop freely")

data_cohes$pcohes03 <- set_label(x=data_cohes$pcohes03, label= "Share values")

data_cohes$pcohes04 <- set_label(x=data_cohes$pcohes04, label= "Different cultures")

data_cohes$pcohes05 <- set_label(x=data_cohes$pcohes05, label= "Law & order")

data_cohes$pcohes06 <-  set_label(x=data_cohes$pcohes06, label= "Live as wanted")

data_cohes$pcohes07 <-  set_label(x=data_cohes$pcohes07, label= "Compromises worked out")

data_cohes$pcohes08 <-  set_label(x=data_cohes$pcohes08, label= "Clear leadership")

data_cohes$pcohes09 <-  set_label(x=data_cohes$pcohes09, label= "Tight links")

data_cohes$pcohes10 <-  set_label(x=data_cohes$pcohes10, label= "Live freely")

data_cohes$pcohes11 <-  set_label(x=data_cohes$pcohes11, label= "Political influence")

data_cohes$pcohes12 <-  set_label(x=data_cohes$pcohes12, label= "Self restrict")


```


Check labels

```{r}
view_df(data_cohes)
```


# Patterns of careless respondents (with library `responsePatterns`)

Within subject autocorrelation

```{r eval=FALSE}
rp <- data_cohes %>% dplyr::select(-pid) %>%  responsePatterns::rp.acors(., max.lag = 5, na.rm = TRUE)
rp.hist(rp)
save(rp, file="processing/objects/rp.Rdata")
```
* This takes a while, the object is saved in processing/objects and the chunk is switched off (eval=FALSE)


Generate careless indexes and merge with the original data in data_patterns object

```{r}
load("02-processing/objects/rp.Rdata")
indices <- rp.indices(rp, round = 2, include.coefs = F)

data_patterns <-cbind(data_cohes,rp@coefficients, rp@indices)
names(data_patterns)


```


Explore and define careless respondents:
```{r}
data_patterns %>%  arrange(desc(sum.abs.ac)) %>% slice(1:20)

careless <- data_patterns %>%  arrange(desc(sum.abs.ac)) %>% filter(sum.abs.ac>=4)

dim(careless)
```


Generate careless filter = 1

```{r}
data_patterns <-data_patterns %>% mutate(careless = ifelse(sum.abs.ac > 4, 1, 0))
frq(data_patterns$careless)

# generate dataframe with careless
data_cohes_panel <- data_patterns %>% dplyr::select(pid, pcohes01:pcohes12,careless)```


# Save dataset

```{r}
save(data_cohes_panel, file="01-input/data/proc/data_cohes_panel.Rdata")
```
