---
title: "latent class - Pilot study"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
      number_sections: yes
    code_folding: show
    number_sections: yes
editor_options:
  chunk_output_type: console
---

# Libraries

```{r}
pacman::p_load(dplyr, poLCA, sjmisc, psych,sjlabelled)
```


# Data & Recodes

Dicothomizing (for clear interpretation, alternative explor polythomous latent class and/or latent profile analysis later)

```{r}
load("01-input/data/proc/data_cohes_pilot.Rdata")
names(data_cohes_pilot)
data_cohes_dic <-  data_cohes_pilot %>% dplyr::select(-pid,-careless) %>% 
  rec(rec = "1,2,3=1; 4,5=2",
      val.labels = c("low", "high"), suffix = "") 

frq(data_cohes_dic$pcohes01) # check

alpha(data_cohes_dic)
```



# Explore patterns

```{r}
patterns=table(apply(data_cohes_dic, 1, paste, collapse=""))
patterns_m=as.data.frame(patterns)
patterns_m <- patterns_m[order(-patterns_m$Freq),] 
patterns_m %>% slice(1:10) 

```

# Models estimation

```{r}

names(data_cohes_dic)

f <- cbind(pcohes01,pcohes02,pcohes03,pcohes04,pcohes05,pcohes06,pcohes07,pcohes08,pcohes09,pcohes10)~1

set.seed(1234)
lca1 <- poLCA(f,data_cohes_dic, nclass=1,graphs=F, verbose = FALSE)
set.seed(1234)
lca2 <- poLCA(f,data_cohes_dic, nclass=2,graphs=F, verbose = FALSE)
set.seed(1234)
lca3 <- poLCA(f,data_cohes_dic, nclass=3,graphs=F, verbose = FALSE)
set.seed(1234)
lca4 <- poLCA(f,data_cohes_dic, nclass=4,graphs=F, verbose = FALSE)
set.seed(1234)
lca5 <- poLCA(f,data_cohes_dic, nclass=5,graphs=F, verbose = FALSE)
set.seed(1234)
lca6 <- poLCA(f,data_cohes_dic, nclass=6,graphs=F, verbose = FALSE)
set.seed(1234)
lca7 <- poLCA(f,data_cohes_dic, nclass=7,graphs=F, verbose = FALSE)
```


# Model fit

```{r}
AIC.1 <-as.numeric(lca1$aic)
AIC.2 <-as.numeric(lca2$aic)
AIC.3 <-as.numeric(lca3$aic)
AIC.4 <-as.numeric(lca4$aic)
AIC.5 <-as.numeric(lca5$aic)
AIC.6 <-as.numeric(lca6$aic)
AIC.7 <-as.numeric(lca7$aic)

BIC.1 <-as.numeric(lca1$bic)
BIC.2 <-as.numeric(lca2$bic)
BIC.3 <-as.numeric(lca3$bic)
BIC.4 <-as.numeric(lca4$bic)
BIC.5 <-as.numeric(lca5$bic)
BIC.6 <-as.numeric(lca6$bic)
BIC.7 <-as.numeric(lca7$bic)


llik.1 <-as.numeric(lca1$llik)
llik.2 <-as.numeric(lca2$llik)
llik.3 <-as.numeric(lca3$llik)
llik.4 <-as.numeric(lca4$llik)
llik.5 <-as.numeric(lca5$llik)
llik.6 <-as.numeric(lca6$llik)
llik.7 <-as.numeric(lca7$llik)

chisq.1 <- as.numeric(lca1$Chisq)
chisq.2 <- as.numeric(lca2$Chisq)
chisq.3 <- as.numeric(lca3$Chisq)
chisq.4 <- as.numeric(lca4$Chisq)
chisq.5 <- as.numeric(lca5$Chisq)
chisq.6 <- as.numeric(lca6$Chisq)
chisq.7 <- as.numeric(lca7$Chisq)

G.1 <- as.numeric(lca1$Gsq)
G.2 <- as.numeric(lca2$Gsq)
G.3 <- as.numeric(lca3$Gsq)
G.4 <- as.numeric(lca4$Gsq)
G.5 <- as.numeric(lca5$Gsq)
G.6 <- as.numeric(lca6$Gsq)
G.7 <- as.numeric(lca7$Gsq)

n.obs1 <- as.numeric(lca1$Nobs)
n.obs2 <- as.numeric(lca2$Nobs)
n.obs3 <- as.numeric(lca3$Nobs)
n.obs4 <- as.numeric(lca4$Nobs)
n.obs5 <- as.numeric(lca5$Nobs)
n.obs6 <- as.numeric(lca6$Nobs)
n.obs7 <- as.numeric(lca7$Nobs)

#Creación de Vectores para TABLA DE COMPARACIÓN
AIC <- c(AIC.1, AIC.2,AIC.3,AIC.4,AIC.5, AIC.6, AIC.7)
BIC <- c(BIC.1, BIC.2,BIC.3,BIC.4,BIC.5, BIC.6, BIC.6)
llik <- c(llik.1, llik.2,llik.3,llik.4,llik.5, llik.6, llik.7)
chi.cuadrado <- c(chisq.1, chisq.2,chisq.3,chisq.4,chisq.5, chisq.6, chisq.7)
G2 <- c(G.1, G.2,G.3,G.4,G.5, G.6, G.7)
N <- c(n.obs1, n.obs2,n.obs3,n.obs4,n.obs5, n.obs6, n.obs7)
Modelos <- c("1 clase", "2 clases", "3 clases", "4 clases", "5 clases", "6 clases", "7 clases")
#CREACIÓN TABLA ESTADÍSTICOS DE AJUSTE MODELOS TODAS LAS VARIABLES
fit.indices <- data.frame(Modelos,AIC,BIC,llik,chi.cuadrado,G2,N)
fit.indices
```

From the fit indicators, according t BIC and chi2 4 classes are selected.



# 4 classes

Default:

```{r}
set.seed(1234)
poLCA(f,data_cohes_dic, nclass=4,graphs=T, verbose = FALSE)


```


**Alternative graph 4 class**


```{r, fig.width=10, fig.height=4}
lca4_probs=as.data.frame(lca4$probs)
dim(lca4_probs)
names(lca4_probs)
datlca_tot_par=lca4_probs[c(2,4,6,8,10,12,14,16,18,20)]  # prob only  "yes"
datlca_tot_par$class=c(1:4) # añadir número de clase
library(reshape2)
datlca_tot_parl=melt(datlca_tot_par, id=c("class") )
str(datlca_tot_parl)
print(levels(datlca_tot_parl$variable))

# Relabel factors

get_label(data_cohes_pilot)
datlca_tot_parl$variable=factor(datlca_tot_parl$variable, labels=c(
    "Place in society",
    "Develop freely",
    "Share values",
    "Different cultures",
    "Law & order" ,
    "Live as wanted",
    "Compromises worked out",
    "Clear leadership",
    "Tight links",
    "Live freely"     
    ))
  
  lca4$P # class size
  datlca_tot_parl$class=factor(datlca_tot_parl$class,labels=c("Class 1 (34%)", "Class 2 (35%)", "Class 3 (25%)", "Class 4 (0.04%"))
  library(ggplot2)

lca4_graph <-ggplot(data = datlca_tot_parl, aes(x=variable, y=value, group=class, shape=class)) + 
    geom_line(aes(linetype=class, color=class)) + 
    geom_point(aes(colour=class),size = 4) +
    scale_color_manual(values=c('#F31111','#04129B', '#02971B', '#764080')) +
    ggtitle("Latent class social cohesion") + 
    xlab("Social Cohesión Indicators") + 
    ylab("Conditional probabilities") +
    scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
    theme(text=element_text(family="Arial", size=12),
        plot.caption = element_text(hjust = 0))

lca4_graph
  

```

- CLass 1: liberal
- Class 2: conservative
- Class 3: universal
- Class 4: ...very small

As class 4 is very small, let's try with a 3 class model


# 3 classes

```{r, fig.width=10, fig.height=4}
# Graph latent classes, 3 clases
lca3_probs=as.data.frame(lca3$probs)
dim(lca3_probs)
names(lca3_probs)
datlca_tot_par=lca3_probs[c(2,4,6,8,10,12,14,16,18,20)]  # prob only  "yes"
datlca_tot_par$class=c(1:3) # añadir número de clase
library(reshape2)
datlca_tot_parl=melt(datlca_tot_par, id=c("class") )
str(datlca_tot_parl)
print(levels(datlca_tot_parl$variable))

# Relabel factors

get_label(data_cohes_pilot)
datlca_tot_parl$variable=factor(datlca_tot_parl$variable, labels=c(
    "Place in society",
    "Develop freely",
    "Share values",
    "Different cultures",
    "Law & order" ,
    "Live as wanted",
    "Compromises worked out",
    "Clear leadership",
    "Tight links",
    "Live freely"     
    ))
  
  lca3$P # class size
  datlca_tot_parl$class=factor(datlca_tot_parl$class,labels=c("Class 1 (33%)", "Class 2 (20%)", "Class 3 (46%)"))
  library(ggplot2)

lca3_graph <-ggplot(data = datlca_tot_parl, aes(x=variable, y=value, group=class, shape=class)) + 
    geom_line(aes(linetype=class, color=class)) + 
    geom_point(aes(colour=class),size = 4) +
    scale_color_manual(values=c('#F31111','#04129B', '#02971B')) +
    ggtitle("Latent class social cohesion") + 
    xlab("Social Cohesión Indicators") + 
    ylab("Conditional probabilities") +
    scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
    theme(text=element_text(family="Arial", size=12),
        plot.caption = element_text(hjust = 0))

lca3_graph

```










