---
title: "Analysis"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  html_document:
    toc: yes
    code_folding: hide
    toc_float:
      collapsed: no
      smooth_scroll: false
      number_sections: true
editor_options:
  chunk_output_type: console
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(scipen=9999) # desactivar notacion cientifica
```


# Objective

Exploratory underlying dimensions (EFA) 


# Libraries

```{r}
# if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,       # Manipulacion de datos
               sjmisc,      # descriptivos y frecuencias
               sjPlot,      # tablas, plots y descriptivos
               responsePatterns, # detect careless resp.
               corrplot,     # plot correlacion
               psych, # EFA
               EFAutilities, #EFA
               lavaan  # CFA
               )
```


# Pilot study


## Data

```{r}
load(file = "01-input/data/proc/data_cohes_pilot.Rdata" )
names(data_cohes_pilot)
# stargazer(as.data.frame(data_cohes), type="text")
```


## Bivariate

```{r}
data_cohes_pilot %>% select(pcohes05,pcohes07,pcohes02, pcohes09, pcohes04,pcohes01,pcohes10,pcohes06,pcohes03,pcohes08) %>% plot_likert(.,
  values = "sum.outside",
  show.prc.sign = TRUE,
  reverse.scale = TRUE,
  expand.grid = T,
  catcount = 5,
  show.n = FALSE,
  geom.colors = "BuPu")


M_pilot <- cor(na.omit(data_cohes_pilot %>% select(pcohes01:pcohes10)))

corrplot.mixed(M_pilot)


```

## Factor analysis

```{r}
data_cohes_efa <- data_cohes_pilot %>% select(pcohes01:pcohes10)

M1_pilot <- fa (data_cohes_efa, nfactors=3, rotate="oblimin", fm="ml")
M1_pilot
fa.diagram(M1_pilot, main="Social cohesion battery - pilot study")

```


## fa_table script

```{r}
source("https://raw.githubusercontent.com/franciscowilhelm/r-collection/master/fa_table.R")

tables <- fa_table(M1_pilot)
tables$ind_table
tables$f_table

```


## Alternative (sjPlot - with value labels)

```{r}
data_cohes_pilot %>% select(pcohes02,pcohes04,pcohes07, pcohes01,pcohes03,pcohes05,pcohes08,pcohes09, pcohes06,pcohes10) %>%
sjPlot::tab_fa(., method = "ml", nmbr.fctr = 3, rotation = "varimax", alternate.rows = FALSE)
```


Conclusion: there is a three factor structure in the pilot data, now we will compare this underlying structure with the panel data.


# Panel study - first wave

## Data

```{r}
load(file = "01-input/data/proc/data_cohes_panel.Rdata" )
names(data_cohes_panel)
# stargazer(as.data.frame(data_cohes), type="text")
```

**Note**: The social cohesion battery in the panel study has 2 more items (11 & 12), they are excluded from the following analysis for the sake of comparison with the pilot study.


## Bivariate

```{r}
data_cohes_panel %>% select(pcohes05,pcohes02,pcohes07, pcohes09, pcohes04,pcohes01,pcohes10,pcohes06,pcohes03,pcohes08) %>% plot_likert(.,
  values = "sum.outside",
  show.prc.sign = TRUE,
  reverse.scale = TRUE,
  expand.grid = T,
  catcount = 5,
  show.n = FALSE,
  geom.colors = "BuPu")


M_panel <- cor(na.omit(data_cohes_panel %>% select(pcohes01:pcohes12)))

corrplot.mixed(M_panel)

```


## Factor analysis

```{r}
efa_panel <- data_cohes_panel %>% select(pcohes01:pcohes12)

M1_panel <- fa (efa_panel, nfactors=3, rotate="oblimin", fm="ml")
M1_panel
fa.diagram(M1_panel, main="Social cohesion battery - pilot study")

```


## fa_table script

```{r}
source("https://raw.githubusercontent.com/franciscowilhelm/r-collection/master/fa_table.R")

tables_panel <- fa_table(M1_panel)
tables_panel$ind_table
tables_panel$f_table

```


## Alternative (sjPlot)

```{r}
data_cohes_panel %>% select(pcohes02,pcohes04,pcohes07,pcohes11,pcohes12, pcohes01,pcohes03,pcohes05,pcohes08,pcohes09, pcohes06,pcohes10) %>%
sjPlot::tab_fa(., method = "ml", nmbr.fctr = 3, rotation = "varimax", alternate.rows = FALSE)
```


# General conclusion

The factor structrue is consistent between the pilot and the panel study. Three main factors are extracted, which could be named as "universal values", "traditional" and "free-riders". 

Next: 
- get factor scores and proceed to regression models. 
- graphical representation of the prevalece of the three dimensions at territorial level (map).



